---
title: "bat_speed"
author: "Diego Martinez"
date: "6/5/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, cache = TRUE)

library(dplyr)
library(tidyverse)
library(broom)
library(tidyverse)
library(skimr)
library(gt)




metrics<-read_csv("metrics.csv")

max_evs<-read_csv("max_evs.csv")

# for loop for how I determined the launch angle at which players maximizes
# their exit velo. Takes awhile so I saved the results and they can be found
# above in max_evs.csv.

# Prior to this step I arranged the players by name and season, and then I
# arranged by launch angle. Their were 2376 player-seasons in the dataset

# for (j in 1:2376) {
#   player <-player_season%>%
#     filter(player_number == j)
#   
#   x = tibble()

# inner loop that finds and saves the the maximum exit velo for a given window.
# The window size is # rows/8.

#   for (i in 1:(nrow(player)-round((nrow(player)/8)))) {
#     y<-player%>%
#             slice(i:(i+round((nrow(player)/8))))%>%
#       mutate(avg_ev = mean(launch_speed),
#              avg_la = mean(launch_angle))
#     
# for each player keeps the window with highest EV.
#
#     x<-x%>%bind_rows(y)%>%
#       filter(avg_ev == max(avg_ev))
#   
#   }
#
# collection of the max ev windows for each player 
#
#   max_evs<-max_evs%>%bind_rows(x)
# }



```


```{r building metrics dataset, eval=FALSE, echo=FALSE}

people<-read_csv("People.csv") 

ids_copy <- read_csv("ids copy.csv")%>%
  select(FANGRAPHSNAME, IDFANGRAPHS, bbrefID = BREFID)

people<-people%>%left_join(ids_copy, by = "bbrefID")%>%
  mutate(playerid = as.numeric(IDFANGRAPHS))%>%
  select(weight, height, playerid)%>%
  filter(!is.na(playerid))


advanced <- read_csv("advanced.csv")
batted_ball <- read_csv("batted_ball.csv")


ages <- read_csv("ages.csv")%>%
  select(Season, Name, Age, playerid)

ids<- read_csv("ids copy.csv")

ids<-ids%>%select(IDFANGRAPHS,MLBID)%>%
  mutate(playerid = as.numeric(IDFANGRAPHS), batter = MLBID)
  

defense <- read_csv("defense.csv")

plate_disc<-read_csv("plate_disc.csv")%>%
  mutate_if(is.character,topct)%>%
  select(-Team, -Name)

defense<-defense%>%
  select(playerid, Pos, GS)%>%
  group_by(playerid, Pos)%>%
  mutate(total_g = sum(GS))%>%
  arrange(playerid, desc(total_g))%>%
  ungroup()%>%
  group_by(playerid)%>%
  top_n(n =1)%>%
  select(playerid, Pos)%>%
  unique()


fangraphs<-ages%>%
  left_join(advanced, by = c("playerid", "Season"))%>%
  left_join(batted_ball, by = c("playerid", "Season"))%>%
  left_join(ids, by = "playerid")%>%
  left_join(defense, by = "playerid")%>%
  left_join(plate_disc, by = c("playerid", "Season"))%>%
  left_join(people, by = "playerid")

metrics<-fangraphs%>%
  select(Season,Name, Age, playerid, PA, `K%`, ISO, wOBA,`LD%`,`GB%`,`FB%`,`Soft%`,`Med%`,`Hard%`, batter, Pos, height, weight)%>%
  mutate(game_year = Season, player_name = Name)%>%
  select(-Season, -Name, -player_name)%>%
  filter(!is.na(batter))
  
```

# Bat Speed Aging Curve 

Exit Velocity Equation from Alan Nathan:

$ev = ea*vball + (1+ea)*vbat$


$vbat = (ev - ea*vball)/(1+ea)$

I followed the methods Marhsall used in the article about Reverse Enginnering Swing Mechanics. I differed in increasing my sample size to included players with at least 50 Batted Ball Events, not only 100. I computed ea linearly from EV for each plyer. I also calibrated ea each hitter by estimating that the average of the top 10% of BBE by exit velocity. These I corresponded to ea =0.20 and the average of the bottom 10% of BBE by exit velocity I corresponded to ea = -0.1 for each player. I then filled in the rest linearly. My range for bat speed was higher than Marshalls and Aucoins, presumably by how I calibrated ea. 
##Highest Bat Speeds 

```{r Calculating bat speed}


swing_speeds_all<-max_evs%>%
  
  # need pitch speed for the bat speed equation 
  
  filter(!is.na(release_speed))%>%
  
  # Alan Nathan found pitch speed decreases 8.4% by time reaches plate. Assuming ea = 0.2, the maximum, "barreled" "flush" contact. 
  
  mutate(v_ball = 0.916*release_speed,
        
         ea = .2,
         bat_speed = (launch_speed-(ea*v_ball))/(1+ea))%>%
  
  # joining to include woba as well as age, height, position metrics into dataset. 
  
  left_join(metrics, by = c("game_year", "batter"))


avg_speeds_indiv<-swing_speeds_all%>%
  group_by(game_year, player_name)%>%
  
  # extreme values and outliers that happen to fall in the window of maximum exit velo
  
  filter(bat_speed > 65)%>%
  
  # various summary statistics for each player's bat speed 
  
  mutate(avg_speed = mean(bat_speed), 
         med_speed = median(bat_speed), 
         avg_ev = mean(launch_speed), 
         three_fourths = quantile(bat_speed, probs = 0.75),
         min = min(bat_speed), 
         max = max(bat_speed))%>%
  arrange(desc(avg_speed))%>%
  select(game_year, player_name, Age, avg_speed, three_fourths, avg_ev, med_speed, PA, wOBA, Pos, height, weight)%>%
  unique()%>%
    filter(!is.na(Age))%>%

  # grouping RF and LF together.
  
  mutate(Pos = case_when(Pos %in% c("RF", "LF") ~ "Corner OF",
                         TRUE ~ Pos))%>%
  arrange(desc(avg_speed))

```

```{r min/max speeds}

# code to create tables for highest and lowest average bat speeds using head and
# tail functions

as_tibble(head(avg_speeds_indiv%>%
                 mutate(avg_bat_speed = avg_speed)%>%
                 select(-three_fourths, -med_speed, -avg_speed, -avg_ev, -Pos, -height, -weight), 10))%>%
  gt()%>%
  fmt_number(columns = "avg_bat_speed",decimals = 2)


as_tibble(tail(avg_speeds_indiv%>%
                 mutate(avg_bat_speed = avg_speed)%>%
                 select(-three_fourths, -med_speed, -avg_speed, -avg_ev, -Pos, -height, -weight), 10))%>%
  gt()%>%
  fmt_number(columns = "avg_bat_speed",decimals = 2)

```

```{r}

avg_speeds_indiv%>%
  ggplot(aes(x = Age, y = avg_speed)) + geom_point() + geom_smooth()


avg_speeds_indiv%>%
  filter(Age < 38, Age >19) %>%
  ggplot(aes(x = Age, y = avg_speed)) + geom_point() + geom_smooth(method = 'gam', formula = y ~ s(x))
```


```{r general aging curve set up}

# need two consecutive seasons for delta method. dataset for joining current
# season to previous season numbers

season_2<-avg_speeds_indiv %>%
  mutate(game_year = game_year + 1)%>%
  select(-Pos)
colnames(season_2)[c(3:9)] = paste(colnames(season_2)[c(3:9)], 't1', sep = '_')

# bat_speed deltas 

indiv_delta<-avg_speeds_indiv%>%
  arrange(player_name, desc(game_year))%>%
  
  # joing previous season data 
  
  left_join(season_2, by = c("game_year", "player_name"))%>%
  
  # making sure the year and age is consecutive
  
  filter(!is.na(Age_t1), Age == Age_t1 + 1)%>%
  ungroup()%>%
  
  # creating age bins and the difference for each players bat speed year to year
  
  mutate(bins = paste(Age_t1, Age, sep = "/"),
         delta = avg_speed - avg_speed_t1)%>%
  group_by(bins, Age)%>%
  
  # average delta for each age bin
  
  summarise(n = n(),
            sum = sum(delta),
         avg_delta = mean(delta))%>%
  ungroup()


indiv_delta%>%
    filter(Age > 23, Age < 35)%>%
  arrange(Age)%>%
  # ungroup()%>%
  # mutate(csum = cumsum(avg_delta),
  #        max = csum - max(csum))%>%
  # select(-sum, -max, -Age)%>%
  gt()%>%fmt_number(columns = c("avg_delta"), decimals = 4)



# indiv_delta%>%
#     filter(Age > 22, Age < 35)%>%
#   arrange(Age)%>%
#   ungroup()%>%
#   mutate(csum = cumsum(avg_diff),
#          max = csum - max(csum))%>%
#   select(-age_avg, -sum, -max, -Age)%>%
#   gt()%>%fmt_number(columns = c("avg_diff", "csum"), decimals = 4)
```

```{r}


csum_delta<-indiv_delta%>%
    filter(Age > 20, Age < 39)%>%
  arrange(Age)%>%
  ungroup()%>%
  mutate(csum = cumsum(avg_delta),
         max = csum - max(csum))%>%
  ggplot(aes(x = Age, y = max)) + geom_point()+geom_smooth() +
  scale_x_continuous(breaks = seq(21,38,1)) +
    labs(x = "Age", y = "Change in Bat Speed (MPH)",
       title = "Bat Speed Aging Curve (2015-2019)",
       subtitle = "Cumulative Sum, 0 = Peak Bat Speed",
       caption = "Red lines signifies >40 players in bin") + 
    geom_vline(xintercept  = 24, linetype = "dotted", color = "red") + geom_vline(xintercept = 34, linetype = "dotted", color = "red")
  


  
change_delta<-indiv_delta%>%
  filter(Age > 23, Age < 35)%>%
  arrange(Age)%>%
  ggplot()+geom_col(aes(x = bins, y = avg_delta, fill = avg_delta)) +   scale_fill_continuous(low = "red", high = "green", guide = FALSE) + 
  labs(x = "Age", y = "Avg Change in Bat Speed (MPH)",
       title = "Average Change in Bat Speed By Age (2015-2019)") 



cowplot::plot_grid(change_delta, csum_delta)

change_delta
csum_delta

```

```{r}



avg_speeds_indiv%>%
  arrange(player_name, desc(game_year))%>%
  group_by(player_name)%>%
  left_join(season_2, by = c("game_year", "player_name"))%>%
  filter(!is.na(Age_t1), Age == Age_t1 + 1)%>%
  mutate(bins = paste(Age, Age_t1, sep = "/"),
         dif = avg_speed - avg_speed_t1)%>% 
  filter(Age > 24, Age< 34, Pos != "P")%>%
  group_by(bins, Age, Pos)%>%
  summarise(n = n(),
         sum = sum(dif),
         avg_diff = mean(dif))%>%
   ungroup()%>%
  arrange(Pos, Age)%>%
  group_by(Pos)%>%
  mutate(csum = cumsum(avg_diff),
         max = csum - max(csum))%>%
  ggplot(aes(x = Age, y = max)) + geom_point()+geom_smooth(se = FALSE) +
  scale_x_continuous(breaks = seq(20,42,1)) + 
  labs(x = "Age", y = "Avg Change in Bat Speed (MPH)",
       title = "Average Change in Bat Speed (15-19)") + facet_wrap(~Pos) + 
  theme(axis.text.x = element_text(angle = 90)) +
  scale_y_continuous(limits = c(-2,0), breaks = seq(-2,0,0.2))


```


```{r}
heights<-swing_speeds_all%>%
  group_by(game_year, player_name)%>%
  filter(bat_speed > 65)%>%
  mutate(avg_speed = mean(bat_speed), med_speed = median(bat_speed), avg_ev = mean(launch_speed), fourths = quantile(bat_speed, probs = 0.75), min = min(bat_speed), max = max(bat_speed))%>%
  arrange(desc(avg_speed))%>%
  select(game_year, player_name, Age, avg_speed, fourths, avg_ev, med_speed, PA, wOBA, height, weight)%>%
  unique()%>%
    filter(!is.na(Age))

avg_speeds_heights<-heights%>%
  mutate(height_group = case_when(height < 73 ~ "-6'0",
                            height < 76 ~ "6'1 - 6'3",
                            height >= 76 ~ "6'4-"))%>%
  bind_rows(heights%>%mutate(height_group = case_when(height < 72 ~ "Under 6'0",
                            height < 75 ~ "6'1 - 6'2",
                            height >= 75 ~ "6'3-")))


season_heights<-avg_speeds_heights %>%
  mutate(game_year = game_year + 1)%>%
  select(-height_group, - height, -weight)

colnames(season_heights)[c(3:9)] = paste(colnames(season_heights)[c(3:9)], 't1', sep = '_')


avg_speeds_heights%>%
  arrange(player_name, desc(game_year))%>%
  group_by(player_name)%>%
  left_join(season_heights, by = c("game_year", "player_name"))%>%
  filter(!is.na(Age_t1), Age == Age_t1 + 1)%>%
  mutate(bins = paste(Age, Age_t1, sep = "/"),
         dif = avg_speed - avg_speed_t1)%>% 
  filter(Age > 22, Age<35, height_group%in% c("-6'0", "6'1 - 6'3", "6'3-", "6'4-"))%>%
  group_by(bins, Age, height_group)%>%
  summarise(n = n(),
         sum = sum(dif),
         avg_diff = mean(dif))%>%
   ungroup()%>%
  arrange(height_group, Age)%>%
 group_by(height_group)%>%
  mutate(csum = cumsum(avg_diff),
         max = csum - max(csum))%>%
  filter(Age > 22, Age< 38)%>%
  ggplot(aes(x = Age, y = max)) + geom_point()+geom_smooth(se = FALSE) +
  scale_x_continuous(breaks = seq(20,42,1)) + 
  labs(x = "Age", y = "Avg Change in Bat Speed (MPH)",
       title = "Average Change in Bat Speed (15-19)") + 
  facet_wrap(~height_group) + 
  theme(axis.text.x = element_text(angle = 90)) +
  scale_y_continuous(limits = c(-2,0), breaks = seq(-2,0,0.2))
```



###imputed
```{r imputed}


season_2<-avg_speeds_indiv_2 %>%
  mutate(Age = Age + 1)%>%
  ungroup()%>%
  select(- game_year, -Pos, - height, -weight)
colnames(season_2)[c(3:8)] = paste(colnames(season_2)[c(3:8)], 't1', sep = '_')


indiv_delta_3<-avg_speeds_indiv_2%>%
  arrange(player_name, desc(game_year))%>%
  group_by(player_name)%>%
  left_join(season_2, by = c("Age", "player_name"))%>%
  ungroup()%>%
  select(-PA_t1, -wOBA_t1, - wOBA)


      
            
library(mice)

imputed<- mice(indiv_delta_3%>%select(-player_name, -fourths_t1, -avg_ev_t1, - Pos, -height, -weight))



new_imp<-map_dfr(1:5, ~complete(imputed, action = .x))

new_imp<-indiv_delta_3%>%
  bind_rows(indiv_delta_3)%>%
  bind_rows(indiv_delta_3)%>%
  bind_rows(indiv_delta_3)%>%
  bind_rows(indiv_delta_3)%>%
  select(player_name, Pos, height, weight)%>%
  bind_cols(new_imp)%>%
  group_by(player_name, game_year, Age, Pos)%>%
  summarise_all(mean)%>%
  mutate(Age_t1 = Age -1)
  


imputed_delta<-new_imp%>%
  arrange(player_name, desc(game_year))%>%
  group_by(player_name)%>%
  filter(!is.na(Age_t1), Age == Age_t1 + 1)%>%
  ungroup()%>%
  mutate(bins = paste(Age_t1, Age, sep = "/"),
         dif = avg_speed - avg_speed_t1,
         player_name = player_name)%>%
  group_by(bins, Age)%>%
  summarise(n = n(),
            sum = sum(dif),
         avg_diff = mean(dif))%>%
  ungroup()




imputed_delta

csum_delta_3<-imputed_delta%>%
    filter(Age > 21, Age < 39)%>%
  arrange(Age)%>%
  ungroup()%>%
   mutate(csum = cumsum(avg_diff),
         max = csum - max(csum))%>%
  ggplot(aes(x = Age, y = max)) + geom_point()+geom_smooth(method = "gam") +
  scale_x_continuous(breaks = seq(22,40,1)) +
   scale_y_continuous(limits = c(-2,0), breaks = seq(-2,0,0.2)) + 
  labs(x = "Age", y = "Csum Bat Speed (MPH)",
       title = "Cumulative Sum Bat Speed (15-19)")



change_delta_3<-imputed_delta%>%
  filter(Age > 21, Age < 39)%>%
  arrange(Age)%>%
  ggplot()+geom_col(aes(x = Age, y = avg_diff, fill = avg_diff)) +   scale_fill_continuous(low = "red", high = "green", guide = FALSE) + 
  scale_x_continuous(breaks = seq(22,38,1)) +
  labs(x = "Age", y = "Avg Change in Bat Speed (MPH)",
       title = "Average Change in Bat Speed By Age (2015-2019)") 
  
imputed_delta
cowplot::plot_grid(change_delta_3, csum_delta_3)

change_delta_3
csum_delta_3


new_imp%>%
  arrange(player_name, desc(game_year))%>%
  group_by(player_name)%>%
  filter(!is.na(Age_t1), Age == Age_t1 + 1)%>%
  mutate(bins = paste(Age, Age_t1, sep = "/"),
         dif = avg_speed - avg_speed_t1)%>% 
  group_by(bins, Age, Pos)%>%
  summarise(n = n(),
            avg_speed = mean(avg_speed_t1),
         sum = sum(dif),
         avg_diff = mean(dif))%>%
   ungroup()%>%
  filter(Age > 22, Age< 35, Pos != "P")%>%
  group_by(Pos)%>%
  arrange(Pos, Age)%>%
  mutate(csum = cumsum(avg_diff),
         max = csum - max(csum))%>%
  ggplot(aes(x = Age, y = max)) + geom_point()+geom_smooth(se = FALSE) +
  scale_x_continuous(breaks = seq(22,36,1)) + 
  labs(x = "Age", y = "Avg Change in Bat Speed (MPH)",
       title = "Average Change in Bat Speed (15-19)") + facet_wrap(~Pos) + 
  theme(axis.text.x = element_text(angle = 90)) + scale_y_continuous(limits = c(-2,0), breaks = seq(-2,0,0.2))

```

```{r}
bat_group<-new_imp%>%
  arrange(game_year)%>%
  group_by(player_name)%>%
  mutate(min_age = min(Age_t1))%>%
  #filter(min_age >= 25 & min_age < 29)%>%
  ungroup()
  

start_speeds<-bat_group%>%filter(Age_t1 == min_age)%>%
  group_by(player_name)%>%
summarise(speed_group = case_when(avg_speed_t1 <= 70 ~ "Below 70 MPH",
       avg_speed_t1 > 70 ~ "Above 70 MPH"))


bat_group%>%
  left_join(start_speeds, by = "player_name")%>%
  filter(!is.na(Age_t1), Age == Age_t1 + 1)%>%
  mutate(bins = paste(Age, Age_t1, sep = "/"),
         dif = avg_speed - avg_speed_t1)%>% 
  group_by(bins, Age, speed_group)%>%
  summarise(n = n(),
         sum = sum(dif),
         avg_diff = mean(dif))%>%
   ungroup()%>%
  arrange(speed_group, Age)%>%
  filter(Age <= 34, Age > 2) %>%
 group_by(speed_group)%>%
  mutate(csum = cumsum(avg_diff),
         max = csum - max(csum))%>%
  ggplot(aes(x = Age, y = max)) + geom_point()+geom_smooth(se = FALSE) +
  scale_x_continuous(breaks = seq(20,42,1)) + 
  labs(x = "Age", y = "Avg Change in Bat Speed (MPH)",
       title = "Average Change in Bat Speed (15-19)") + 
  facet_wrap(~speed_group) + 
  theme(axis.text.x = element_text(angle = 90)) 
#+ scale_y_continuous(limits = c(-2,0), breaks = seq(-2,0,0.2))
  
  
  
  
```

```{r}
bat_group<-avg_speeds_indiv%>%
  arrange(player_name, game_year)%>%
  left_join(season_2%>%select(-height, -weight), by = c("game_year", "player_name"))%>%
  filter(!is.na(Age_t1), Age == Age_t1 + 1)%>%
  group_by(player_name)%>%
  mutate(min_age = min(Age_t1))%>%
  filter(min_age >= 23 & min_age <= 25)%>%
  ungroup()

quantile(bat_group$avg_speed_t1)


start_speeds<-bat_group%>%filter(Age_t1 == min_age)%>%
  group_by(player_name)%>%
summarise(speed_group = case_when(avg_speed_t1 <= median(bat_group$avg_speed_t1) ~ "Below Median ",
       avg_speed_t1 > median(bat_group$avg_speed_t1) ~ "Above 70 MPH"))

start_speeds%>%count(speed_group)

bat_group%>%
  left_join(start_speeds, by = "player_name")%>%
  filter(!is.na(Age_t1), Age == Age_t1 + 1)%>%
  mutate(bins = paste(Age, Age_t1, sep = "/"),
         dif = avg_speed - avg_speed_t1)%>% 
  group_by(bins, Age, speed_group)%>%
  summarise(n = n(),
         sum = sum(dif),
         avg_diff = mean(dif))%>%
   ungroup()%>%
  group_by(speed_group)%>%
  mutate(csum = cumsum(avg_diff),
         max = csum - max(csum))%>%
  ggplot(aes(x = Age, y = max)) + geom_point()+geom_smooth(se = FALSE) +
  #scale_x_continuous(breaks = seq(20,42,1)) + 
  labs(x = "Age", y = "Avg Change in Bat Speed (MPH)",
       title = "Bat Speed Grouped By First Recorded Bat Speed (2015-2019)",
       subtitle = "0 = Peak Bat Speed") + 
  facet_wrap(~speed_group) + 
  theme(axis.text.x = element_text(angle = 90)) 
  


  
  bat_group%>%
  left_join(start_speeds, by = "player_name")%>%
  filter(!is.na(Age_t1), Age == Age_t1 + 1)%>%
  mutate(bins = paste(Age, Age_t1, sep = "/"),
         dif = avg_speed - avg_speed_t1)%>% 
  group_by(bins, Age, speed_group)%>%
  summarise(n = n(),
         sum = sum(dif),
         avg_diff = mean(dif))%>%
   ungroup()%>%
    arrange(speed_group, Age)%>%
  #filter(Age <= 31, Age > 24) %>%
  arrange(Age)%>%
  ggplot()+geom_col(aes(x = bins, y = avg_diff, fill = avg_diff)) +   scale_fill_continuous(low = "red", high = "green", guide = FALSE) + 
  labs(x = "Age", y = "Avg Change in Bat Speed (MPH)",
       title = "Average Change in Bat Speed By Speed Group (2015-2019)") + facet_wrap(~speed_group)
#+ scale_y_continuous(limits = c(-2,0), breaks = seq(-2,0,0.2))
  
  
  
  
```



```{r}
indiv_delta%>%
  filter(Age_t1 <= 35)%>%
  select(-Age_t1, - peak)
```

```{r contact}

metrics_2<-fangraphs%>%
  select(Season,Name, Pos, playerid, Age, PA, `K%`, ISO, wOBA,`LD%`,`GB%`,`FB%`,`Soft%`,`Med%`,`Hard%`, `Contact%`, `SwStr%`)%>%
  mutate(game_year = Season, player_name = Name)%>%
  select(-Season, -Name, -player_name)%>%
  filter(!is.na(`Contact%`))

season_1_con<-metrics_2 %>%
  mutate(game_year = game_year + 1)%>%
  select(-Pos)
colnames(season_1_con)[c(2:14)] = paste(colnames(season_1_con)[c(2:14)], 't1', sep = '_')



metrics_2%>%
  arrange(playerid, desc(game_year))%>%
  group_by(playerid)%>%
  filter(PA > 50)%>%
  left_join(season_1_con, by = c("game_year", "playerid"))%>%
  filter(!is.na(Age_t1), Age == Age_t1 + 1)%>%
  mutate(bins = paste(Age, Age_t1, sep = "/"),
         dif = `Contact%` - `Contact%_t1`)%>% 
  group_by(bins, Age)%>%
  filter(Age <= 36) %>%
  summarise(n = n(),
         sum = sum(dif),
         avg_diff = sum/n)%>%
  filter(Age > 22)%>%
  mutate(csum = cumsum(avg_diff))%>%
  ggplot(aes(x = Age, y = csum)) + geom_point()+geom_smooth(se = FALSE) +
  scale_x_continuous(breaks = seq(20,42,1)) + 
  labs(x = "Age", y = "Avg Change in Contact% (MPH)",
       title = "Average Change in Contact% (15-19)")

```

